Allowing Stable Groups of Prosumers to Enter the Market through Proper Aggregation

### 2014-09-11 Article.tex
upate

In this paper, we focus on how to statistically improve the production stability by carefully forming coalitions of prosumers that have greater probability of staying in acceptable range of production. By using prediction techniques, we form coalitions that meet the contract values ranges proposed by the grid, enabling it to schedule its production accordingly. Meeting contract values for the prosumer are especially relevant in power trade conditions, where energy is traded based on day-ahead predictions. In this context, participants should try to minimize its prediction error in order to maintain a stable state for the grid. They may even occur some penalty if the production deviate from its initial contract value. However, it is pertinent for both side to maintain the production as stable as possible, for the prosumer the stability (with renewable energy source) will impact its net gain and for the power grid its help to maintain its reliability.

>>>>

In this paper, we focus on how to statistically improve the production stability by carefully forming coalitions of prosumers that have greater probability of staying in acceptable range of production. By using prediction techniques, we form coalitions that meet the contract values ranges proposed by the grid, enabling it to schedule its production accordingly. Meeting contract values for the prosumer are especially relevant in power trade conditions, where energy is traded based on day-ahead predictions. In this context, participants should try to minimize its prediction error in order to maintain a stable state for the grid. They may even occur some penalty if the production deviate from its initial contract value. However, it is pertinent for both side to maintain the production as stable as possible, for the prosumer the stability (with renewable energy source) will impact its net gain and for the power grid it helps to maintain its reliability.
